An Automatic Verification Framework for Software Configurations

### 2016-05-09 OSDI/motiv.tex
make correction

\para{Example~4: Singular Value Errors} 
A common error is that a value is set too high or too low.
For example, a parameter relating to memory might be too large,
exhausting the RAM and causing extreme slowness. 
Consider the following real-world misconfiguration file \cite{singleValue}: the
user was experiencing the ``My SQL Server has gone away" error.  
She had the following line in her configuration file.

@@

The user resolved the issue by replacing the above line with {\tt max\_allowed\_packet=20M}. 
It turns out that the original value, 100 MB, is extremely large, a  
statistically anomalous value for the {\tt max\_allowed\_packet} attribute. ConfigV can detect these
outliers. Run on the user's original configuration file, ConfigV would output:

@@

In the above, 104857600 represents the integer value of 100 megabytes.

>>>>

\para{Example~4: Singular Value Errors} 
A common error is that a value is set too high or too low.
For example, a parameter relating to memory might be too large,
exhausting the RAM and causing extreme slowness or even a crash. 
Consider the following real-world misconfiguration file \cite{singleValue}: the
user was experiencing the ``My SQL Server has gone away" error.  
She had the following line in her configuration file.

@@

The user resolved the issue by replacing the above line with {\tt max\_allowed\_packet=2M}. 
It turns out that the original value, 100 MB, is extremely large, a  
statistically anomalous value for the {\tt max\_allowed\_packet} attribute. ConfigV can detect these
outliers. Run on the user's original configuration file, ConfigV would output:

@@

In the above, 104857600 represents the integer value of 100 megabytes. The idea is to give the user
a warning that their value falls outside of a range considered normal and to prompt the  
appropriate adjustments.
